---
title: "Pretest Check Output"
author: "Tyler Leigh"
date: "2/5/2020"
output: html_document
---
``` {r, include=F}
####Libraries####
library(easypackages)
libs<-c("haven", "readr", "tidyverse", "car")
libraries(libs)
####Read in the Data####
dat <- read_sav("Pretest Data.sav")

```

# Frequencies

Note: Response options appear in the first row and frequencies appear in the second row for each variable. Variables are named as they appear in the dataset and are separated by ---------

```{r, echo=F}
####Get out frequencies for all items####
for(x in 1:238){
  cat("-----------", "\n")
  print(attributes(dat[,x])$names)
  print(table(dat[,x]))
  cat("\n", "\n")
}
```

# Correlations

Note: The variables being analyzed appear first in quotes, followed by the raw output of the correlation. P-value is in the second row of the output in line with t-values and degrees of freedom. The actual correlation is at the very bottom of the output for each set of variables.

```{r, echo=F}

print("Party ID and GUNS")
cor.test(dat$P_PARTYID7, dat$GUNS)

print("Party ID and HC5")
cor.test(dat$P_PARTYID7, dat$HC5)

print("Party ID and TRUMP1")
cor.test(dat$P_PARTYID7, dat$TRUMP1)

print("Party ID and THERMTRUMP")
cor.test(dat$P_PARTYID7, dat$THERMTRUMP)

print("Party ID and IDEO")
cor.test(dat$P_PARTYID7, dat$P_IDEO)

print("Party ID and GENMEDTRUST")
cor.test(dat$P_PARTYID7, dat$GENMEDTRUST)


```

